Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-05 ms.tex
give models numerical names in global parameter table
starting update of fitting procedure section

\begin{deluxetable}{rrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{5} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
\PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
\enddata
\end{deluxetable}

@@

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million 
non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
This pixelization is convenient because it is the same format in which the 
\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
resolution maps under consideration. Our procedure will fit the intensity 
measurements in each spatial pixel independently of those in neighboring 
pixels.

>>>>

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61
\enddata
\end{deluxetable}

@@

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. In the case of our full-resolution $6.1'$fits, these parameters
are the SED normalization and the hot dust temperature $T_2$. The same 
formalism will apply to our lower-resolution fits in which $f_1$ is also 
allowed to vary from one line of sight to another.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million 
non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
This pixelization is convenient because it is the same format in which the 
\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
FWHM maps under consideration in our full-resolution fits. Our procedure will 
fit the intensity measurements in each spatial pixel independently of those in 
neighboring pixels.
